---
title: "README"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Columbus AirBnB listing data

We start with extracting the **detailed listing data for Columbus*** via <http://insideairbnb.com/get-the-data.html>.

```{r, echo=FALSE}
library(tibble)
x <- read.csv("data/listings_full.csv")
glimpse(x)
```

A quick `glimpse` at the data shows a total of 96 variables, not all useful, that we need to sort through.

## Define the goal

Being aan Ohio resident, and an AirBnB'er myself, there are some metrics I'm curious about:
* Listing price as determined by location
* Review scores and their distributions
  + Which review metrics have the widest/narrowist distributions?
  + Is one review metric more indicative of others?
  + Are superhosts more likely to receive higher reviews?
  + Does location play a role in average score?
* How many reviews does the average superhost have?
* Average percentage decrease from daily to weekly to monthly between locations
* How does the capacity of a home, number of beds, and number of baths affect pricing?
* How long has the average host been registered?
  + How long has the average superhost been registered?

